---
title: "Analysis of DebateArt Data"
author: "BearMan"
date: '2022-07-13'
output: html_document
---

This is hardly a good analysis, I was just playing with the data I collected from a BS4 webscraper. This was also an excuse to practice my (obviously inexperienced) R/stats skills.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Some setup needed:

```{r}
library(ggplot2)

dartData <- read.csv("DART.csv")
```

## General

Finding the length of the dataset
```{r}
nrow(dartData)
```

## Analysis of Total Arguments

The favored amount of total arguments is 6 or 3 total rounds. The least favored is two total arguments or one total round.

```{r}

ggplot(data=dartData)+
  geom_bar(mapping = aes(x=as.factor(Total.Arguments)))+
  xlab("Total arguments")+
  ylab("Count")+
  labs(title="Distribution of Data in Terms of Total Arguments ")

```




## Analysis of Proportion of Arguments

Note that 1/2 is a full forfeit on one side, 0 is a full forfeit on both sides, and 1 is a complete debate. 

```{r}

ggplot(data=dartData)+
  geom_bar(mapping= aes(x=Proportion.of.Arguments, fill=as.factor(Total.Arguments))) +
  xlab("Completed Arguments/Total Arguments")+
  ylab("Count")+
  labs(title="Count of Proportion of Arguments (with total arguments included)", fill="Total Arguments")

```

The proportion of arguments seems to have some relation with the amount of votes a debate garners. Debates with at least one forfeit have almost double the amount of mean votes when compared to fully completed debates.


```{r}

forfeitRows = dartData[dartData$Proportion.of.Arguments<1,]
mean(forfeitRows$Votes)

nonForfeitRows = dartData[dartData$Proportion.of.Arguments==1,]
mean(nonForfeitRows$Votes)

```

A majority of debates on DART have at least one forfeit:

```{r}
nrow(forfeitRows)
nrow(nonForfeitRows)
```

## Analysis of Comments

A bar chart of the amount of comments on DART.

```{r}
ggplot(data=dartData)+
  geom_bar(mapping = aes(x=Comments))+
  xlab("Comments")+
  ylab("Count")+
  labs(title="Count of Comments")

```


Interestingly, the largest amount of comments on a debate is 384, which is far higher than the mean of 18.

```{r}

max(dartData$Comments)
mean(dartData$Comments)
```



## Analysis of Votes


First, some simple statistics (mean and max):
```{r}
mean(dartData$Votes)
max(dartData$Votes)
```



### Zero Vote Debates

ZVDs make up 6% of all debates. 

```{r}
ZVD <- dartData[dartData$Votes==0,]
nonZVD <- dartData[dartData$Votes!=0,]
nrow(dartData[dartData$Votes==0,]) # Amount
nrow(dartData[dartData$Votes==0,])/nrow(dartData) # Percentage
```


Is this ZVD problem more prevalent in recent times, or is it an older problem? Since this dataset is ordered in a reverse-chronological fashion, we'll classify the first 500 records as "recent" and everything else as "older".

For recent times:

```{r}
recentRows <- dartData[c(0:500),] # Grab 500 most recent records
nrow(recentRows[recentRows$Votes==0,]) # Amount
nrow(recentRows[recentRows$Votes==0,])/nrow(recentRows) # Percentage
```

For older times:
```{r}
oldRows <- dartData[-c(0:500),] # Grab everything else
nrow(oldRows[oldRows$Votes==0,]) # Amount
nrow(oldRows[oldRows$Votes==0,])/nrow(oldRows) # Percentage
```

It seems that the ZVD problem has gotten worse, as the most recent 500 debates house more than 40% of all ZVDs despite only being 25% of the dataset.



#### Characteristics of Zero Vote Debates

ZVDs are less active than debates with votes:
```{r}
mean(ZVD$Comments) # ZVD
mean(nonZVD$Comments) # Non ZVD
```

ZVDs are more complete than the debates with votes:
```{r}
mean(ZVD$Proportion.of.Arguments) # ZVD
mean(nonZVD$Proportion.of.Arguments) # Non ZVD
```

ZVDs are longer than debates with votes:
```{r}
mean(ZVD$Completed.Arguments) # ZVD
mean(nonZVD$Completed.Arguments) # Non ZVD
```




